\documentclass{ws-mpla}
\usepackage[super,compress]{cite}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=black,citecolor=black,linkcolor=black,filecolor=black}
\usepackage{breakurl}
\begin{document}

\thispagestyle{plain}

\title{Bib\TeX\/ing in MPLA style}

\markboth{WSPC}{Using World Scientific's style file}

\maketitle

\section{Usage}

\begin{verbatim}
\documentclass{ws-mpla}
\usepackage{url}
\begin{document}
Sample output using ws-mpla bibliography style file ...
...text.\cite{best,pier,jame} ...
\bibliographystyle{ws-mpla}
\bibliography{sample}
\end{document}
\end{verbatim}

\section{Output}
Sample output using ws-mpla bibliography style file

\begin{enumerate}
\item article: ...text.\cite{best,pier,jame,atlas,ATLAS-CONF-2012-029}

\item proceedings: ...text.\cite{Weiss94}

\item inproceedings: ...text.\cite{conftypical,CantoneCP90}

\item book: ...text.\cite{ArmsRace1}

\item edition: ...text.\cite{ComplexVariables}

\item editor: ...text.\cite{ColBenh:93}

\item series: ...text.\cite{inbook}

\item tech report: ...text.\cite{hobby1992,CSTR116}

\item unpublished: ...text.\cite{VoQS,ATLAS-CONF-2011-011,ATLAS-CONF-2011-121}

\item phd thesis: ...text.\cite{Brown:1988:IEL}

\item masters thesis: ...text.\cite{segms}

\item incollection: ...text.\cite{Jones:Phoneme}

\item booklet: ...text.\cite{URW:kerning}

\item misc: When the reference forms part of the sentence, it should not
be typed in superscripts, e.g.: ``One can show from
Ref.~\refcite{netpbm} that $\ldots$''
\end{enumerate}

References are to be listed in the order cited in the text in Arabic
numerals.  They can be typed in superscripts after full stop and comma but before other
punctuation marks,
e.g.~``$\ldots$ in the statement.\cite{segms}  $\ldots$ in the statement\cite{segms};'' or used directly,
e.g.~``see Ref.~\refcite{Bohr} for examples.''  Please list using the
style shown in the following examples.  For journal names, use the
standard abbreviations.  Typeset references in 9 pt Times Roman.
Each reference number should consist of one reference only.

\bibliographystyle{ws-mpla}
\bibliography{sample}
\end{document} 